Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-11-19 docs/Truman/LocalConservation/paper/paper.tex
Minor updates to bibliography

Recall the main line of analysis in {\color{red}(supposed to be Brezzi?)}\cite{} leading to the construction of robust
test norms. With the robust test norms, we have
\begin{equation}
\begin{array}{ll}
   \LRp{\Vert u - u_h \Vert^2+ \Vert \bfsig - \bfsig_h
   \Vert^2}^{\frac{1}{2}}
& \lesssim \Vert (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h \Vert_E \\[8pt]
&= \inf_{(v_h,\bftau_h,\hat{v},\hat{r}_h)}
\Vert (u - v_h, \bfsig - \bftau_h, \hat{u} - \hat{v}_h, \hat{t} - \hat{r}_h \Vert_E
\end{array}
\end{equation}
The last equality follows from the fact that DPG method delivers the best approximation
error in the energy norm (minimizes the residual). This is not longer true for the
restricted version. So, can we claim the robustness in the sense of the inequality above
for the restricted version as well?

>>>>

Recall the main line of analysis in {\color{red}(supposed to be Brezzi?)}\cite{} leading to the construction of robust
test norms. With the robust test norms, we have
\begin{equation}
\begin{array}{ll}
   \LRp{\Vert u - u_h \Vert^2+ \Vert \bfsig - \bfsig_h
   \Vert^2}^{\frac{1}{2}}
& \lesssim \Vert (u - u_h, \bfsig - \bfsig_h, \hat{u} - \hat{u}_h, \hat{t} - \hat{t}_h \Vert_E \\[8pt]
&= \inf_{(v_h,\bftau_h,\hat{v},\hat{r}_h)}
\Vert (u - v_h, \bfsig - \bftau_h, \hat{u} - \hat{v}_h, \hat{t} - \hat{r}_h \Vert_E
\end{array}
\end{equation}
The last equality follows from the fact that DPG method delivers the best approximation
error in the energy norm (minimizes the residual). This is no longer true for the
restricted version. So, can we claim robustness in the sense of the inequality above
for the restricted version as well?
